X-ray phase-contrast imaging at \SI{100}{\kilo\electronvolt} on conventional sources

### 2013-10-24 hedpc_natphys.tex
thomas review of the changes

The vast majority of phase-sensitive techniques, including crystal analyzer
based~\cite{Davis1995,Chapman1997} or interferometric~\cite{Bonse1965,Momose1996}
methods rely on X-ray beams of high spatial and temporal coherence, which is
available only at synchrotron sources. Inline
phase contrast~\cite{Snigirev1995,Wilkins1996,Cloetens1996} and
Talbot interferometry~\cite{Cloetens1997,David2002,Momose2003a} need high
spatial coherence but are available on microfocus sources.
Phase-contrast imaging using X-ray beams of low temporal \emph{and}
spatial coherence such as conventional low-brilliance X-ray tubes have been
demonstrated with coded
apertures~\cite{Munro2012} and Talbot-Lau
interferometry~\cite{Pfeiffer2006}. Analyzer-based systems have been
recently extended to tube sources~\cite{Nesch2009,Parham2009}
but the photon energy is limited
to the tungsten $K_\alpha$ line at~\SI{60}{\kilo\eV}.
In addition to phase sensitivity, these techniques provide a dark-field
contrast, also called scatter contrast or visibility-reduction contrast,
that is proportional to the integrated local small angle scattering power
from microscopic density fluctuations in a specimen~\cite{Pfeiffer2008}.

@@

Here, we introduce a method for phase-contrast imaging which is
compatible with the entire diagnostic energy range of X-rays, 
compact imaging arrangements and 
conventional X-ray tubes. The method is based on Talbot-Lau interferometry~\cite{Pfeiffer2006} and employs an edge-on approach for the grating design and
arrangement. 
The challenge which limited the progress towards higher energies was mainly
related to the manufacturing of gratings with high aspect ratios. The aspect
ratio, given by
\begin{equation}
    \text{R} = \frac{2h}{p},
\end{equation}
where $p$ is the grating period and $h$ the  structure
height, is normally limited by the lithographic process, as grating
structures tend to collapse or deform (e.g. due to capillary forces) if
the aspect ratio is too high. For a given setup length these parameters
depend on the target energy $E$ according to $p \propto
1/\sqrt{E}$ and $h \propto E^3$, and therefore $\textnormal{R}
\propto E^{7/2}$~\cite{Momose2003a}. If at $E=\SI{25}{\kilo\electronvolt}$ an aspect ratio
for the absorption grating around $\textnormal{R}=30$ is necessary for a
reasonable length of the experimental arrangement, it would have to be at
least $128$ for $E=\SI{100}{\kilo\electronvolt}$. Moreover, when using a
broad spectrum, photons above the design energy should also be
efficiently blocked by the gratings, which requires even higher aspect ratios.
The maximum achievable aspect ratios of current fabrication techniques~\cite{David2007,Kenntner2010} are around 60.

@@

Due to the high spectral acceptance~\cite{Weitkamp2005,Thuering2013c} of the
interferometer ($\SI{50}{\kilo\electronvolt}$ to
more than $\SI{160}{\kilo\electronvolt}$) and the high attenuation efficiencies of
the source and analyzer gratings ($>90\%$ up to
$\SI{160}{\kilo\electronvolt}$), the voltage of the X-ray source was set to
the maximum of $\SI{160}{\kilo\volt}$. With a grating structure height of
approximately $\SI{100}{\micro \metre}$, the field of view in the vertical
direction is limited to one detector pixel row. In the horizontal direction,
the field of view is limited by the grating size and the geometric
magnification of the sample, yielding a maximum field of view of
$\SI{30}{\milli\metre}$. In addition to the standard components (source,
camera, interferometer), two optical slits, one in front of the source
grating, the other in front of the camera, were required for the collimation
of the beam in the vertical direction.

Fig.~\ref{Fig:img_chip} shows a radiographic scan of an electronic chip.
Several resistors and an integrated circuits are located on different layers
on the chip. The images were acquired in scanning mode, using a step size of
$\SI{100}{\micro \metre}$ along the $y$ axis. For a better comparison of the
magnified phase and attenuation images, the attenuation image has been
replaced with the differential attenuation image, which was obtained by
digital differentiation. In the attenuation image, the contrast of the soldering points of
the integrated circuit is reduced underneath the resistors, while in
the phase image, they can clearly be identified. The reduced contrast of the 
soldering points in the absorption image is due to beam hardening. The spectrum
impinging on these soldering point is hardened by the resistors in the upper
layer, resuluting in lower absorption contrast. Due to the weaker energy
dependency of phase shifts ($1/E$ compared to $1/E^3$), phase-contrast images
are less sensitive to beam hardening~\cite{Chabior2011a}, which explains the
lower contrast reduction of the soldering points underneath the resistors in the
phase image of the chip. This result shows the benefit of the phase nature in
high-energy X-ray imaging, which may be useful to identify flaws in multilayered
structures such as electronic chips.
\begin{figure}[ht]
    \includegraphics[width=.5\textwidth]{figures/img_chip_dabs.eps}
    \caption{Radiographic scan of an electronic chip. The image was acquired
        with 24 phase steps per line and an exposure time of \SI{15}{\second} per
    step. The top right image shows the differential absorption image.}
    \label{Fig:img_chip}
\end{figure}

@@

In Fig.~\ref{Fig:img_chip}, image acquisition involved 24 phase steps per
line and an exposure time of 15 seconds per step. The long
exposure times are mostly constrained by the low average visibility of the
gratings (\SI{5}{\percent}). The exposure time was chosen in order to
get a low noise in the differential phase image. The \ac{SNR} is
proportional to the visibility and the square root of the exposure
time~\cite{Raupach2011}.
This implies that the exposure times can easily drop by an order of
magnitude as these gratings become comparable in quality to those developed
in the last ten years. 
The detector is also relatively inefficient ($\approx \SI{30}{\percent})$
leaving an additional margin for improvement.

>>>>

The vast majority of phase-sensitive techniques, including crystal analyzer
based~\cite{Davis1995,Chapman1997} or interferometric~\cite{Bonse1965,Momose1996}
methods rely on X-ray beams of high spatial and temporal coherence, which is
available only at synchrotron sources. Inline
phase contrast~\cite{Snigirev1995,Wilkins1996,Cloetens1996} and
Talbot interferometry~\cite{Cloetens1997,David2002,Momose2003a} need high
spatial coherence but are available on polychromatic microfocus sources.
Phase-contrast imaging using X-ray beams of low temporal \emph{and}
spatial coherence such as conventional low-brilliance X-ray tubes have been
demonstrated with coded
apertures~\cite{Munro2012} and Talbot-Lau
interferometry~\cite{Pfeiffer2006}. Analyzer-based systems have been
recently extended to tube sources~\cite{Nesch2009,Parham2009}
but the photon energy is limited
to the tungsten $K_\alpha$ line at~\SI{60}{\kilo\eV}.
In addition to phase sensitivity, these techniques provide a dark-field
contrast, also called scatter contrast or visibility-reduction contrast,
that is proportional to the integrated local small angle scattering power
from microscopic density fluctuations in a specimen~\cite{Pfeiffer2008}.

@@

Here, we introduce a method for phase-contrast imaging which is
compatible with the entire diagnostic energy range of X-rays, 
compact imaging arrangements and 
conventional X-ray tubes. The method is based on Talbot-Lau
interferometry~\cite{Pfeiffer2006} and employs an edge-on illumination approach for the grating design and
arrangement. 
The challenge which limited the progress towards higher energies was mainly
related to the manufacturing of gratings with high aspect ratios. The aspect
ratio, given by
\begin{equation}
    \text{R} = \frac{2h}{p},
\end{equation}
where $p$ is the grating period and $h$ the  structure
height, is normally limited by the lithographic process, as grating
structures tend to collapse or deform (e.g. due to capillary forces) if
the aspect ratio is too high. For a given setup length these parameters
depend on the target energy $E$ according to $p \propto
1/\sqrt{E}$ and $h \propto E^3$, and therefore $\textnormal{R}
\propto E^{7/2}$~\cite{Momose2003a}. If at $E=\SI{25}{\kilo\electronvolt}$ an aspect ratio
for the absorption grating around $\textnormal{R}=30$ is necessary for a
reasonable length of the experimental arrangement, it would have to be at
least $128$ for $E=\SI{100}{\kilo\electronvolt}$. Moreover, when using a
broad spectrum, photons above the design energy should also be
efficiently blocked by the gratings, which requires even higher aspect ratios.
The maximum achievable aspect ratios of current fabrication techniques~\cite{David2007,Kenntner2010} are around 60.

@@

Due to the high spectral acceptance~\cite{Weitkamp2005,Thuering2013c} of the
interferometer ($\SI{50}{\kilo\electronvolt}$ to
more than $\SI{160}{\kilo\electronvolt}$) and the high attenuation efficiencies of
the source and analyzer gratings ($>90\%$ up to
$\SI{160}{\kilo\electronvolt}$), the voltage of the X-ray source was set to
the maximum of $\SI{160}{\kilo\volt}$. With a grating structure height of
approximately $\SI{100}{\micro \metre}$, the field of view in the vertical
direction is limited to one detector pixel row. In the horizontal direction,
the field of view is only limited by the grating size to
$\SI{30}{\milli\metre}$, but wider gratings can be fabricated with this
method and the available technology on larger wafers. In addition to the standard components (source,
camera, interferometer), two optical slits, one in front of the source
grating, the other in front of the camera, were required for the collimation
of the beam in the vertical direction.

Fig.~\ref{Fig:img_chip} shows a radiographic scan of an electronic chip.
Several resistors and an integrated circuits are located on different layers
on the chip. The images were acquired in scanning mode, using a step size of
$\SI{100}{\micro \metre}$ along the $y$ axis. For a better comparison of the
magnified phase and attenuation images, the attenuation image has been
replaced with the differential attenuation image, which was obtained by
digital differentiation. In the attenuation image, the contrast of the soldering points of
the integrated circuit is reduced underneath the resistors, while in
the phase image, they can clearly be identified. The reduced contrast of the 
soldering points in the absorption image is due to beam hardening. The spectrum
impinging on these soldering point is hardened by the resistors in the upper
layer, resulting in lower absorption contrast. Due to the weaker energy
dependency of phase shifts ($1/E$ compared to $1/E^3$), phase-contrast images
are less sensitive to beam hardening~\cite{Chabior2011a}, which explains the
lower contrast reduction of the soldering points underneath the resistors in the
phase image of the chip. This result shows the benefit of the phase nature in
high-energy X-ray imaging, which may be useful to identify flaws in multilayered
structures such as electronic chips.
\begin{figure}[ht]
    \includegraphics[width=.5\textwidth]{figures/img_chip_dabs.eps}
    \caption{Radiographic scan of an electronic chip. The image was acquired
        with 24 phase steps per line and an exposure time of \SI{15}{\second} per
    step. The top right image shows the differential absorption image.}
    \label{Fig:img_chip}
\end{figure}

@@

In Fig.~\ref{Fig:img_chip}, image acquisition involved 24 phase steps per
line and an exposure time of 15 seconds per step. The long
exposure times are mostly constrained by the low average visibility of the
gratings (\SI{5}{\percent}). The exposure time was chosen in order to
get a low noise in the differential phase image. The \ac{SNR} is
proportional to the visibility and the square root of the exposure
time~\cite{Raupach2011}.
This implies that the exposure times can easily drop by an order of
magnitude as these gratings become comparable in quality to those developed
in the last ten years. 
Smaller regions of these gratings actually exhibit a visibility up
to~\SI{14}{\percent} already, indicating that this goal is reachable as the
fabrication becomes more reliable and uniform.
The detector is also relatively inefficient ($\approx \SI{30}{\percent})$
leaving an additional margin for improvement.
